\documentclass{article}

\usepackage[english]{babel}
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{ragged2e}

\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsmath}

\title{Evolutionary Computation - Assignment 10}
\author{
  Patryk Janiak\\
  \texttt{156053}
  \and
  Marek Seget\\
  \texttt{156042}
}

\begin{document}
\maketitle

\section{Problem description}
We are given three columns of integers with a row for each node. The first two columns contain x
and y coordinates of the node positions in a plane. The third column contains node costs. The goal is
to select exactly 50% of the nodes (if the number of nodes is odd we round the number of nodes to
be selected up) and form a Hamiltonian cycle (closed path) through this set of nodes such that the
sum of the total length of the path plus the total cost of the selected nodes is minimized.

\input{algorithms.tex}

\section{Results}

\input{scores.tex}

\input{times.tex}

\input{ls_runs.tex}

\subsection{TSPA.csv}

\input{TSPA.tex}

\subsection{TSPB.csv}

\input{TSPB.tex}

\newpage

\section{Conclusions}

The HEA implementation focused on maximizing efficiency within the fixed time budget defined by MSLS. By incorporating Candidate Lists, the local search speed was improved dramatically, allowing for over 60,000 local search runs compared to fewer than 3,000 in previous iterations. This massive increase in intensification capability was balanced by the Edge Recombination Crossover, which effectively preserved structural information from parents, and a Steady-State population management strategy that strictly enforced diversity to prevent premature convergence.

It achieved the best average objective function scores on both TSPA and TSPB instances, outperforming MSLS, ILS, and LNS. The algorithm also exhibited excellent robustness, with a very narrow spread between the minimum and maximum scores across runs.

Link to the source code:

\url{https://github.com/markopolo139/Evolutionary-computation-put/tree/main/ass10}

The best solutions were checked with the provided solution checker.

\end{document}