\documentclass{article}

\usepackage[english]{babel}
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{ragged2e}

\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsmath}

\title{Evolutionary Computation - Assignment 9}
\author{
  Patryk Janiak\\
  \texttt{156053}
  \and
  Marek Seget\\
  \texttt{156042}
}

\begin{document}
\maketitle

\section{Problem description}
We are given three columns of integers with a row for each node. The first two columns contain x
and y coordinates of the node positions in a plane. The third column contains node costs. The goal is
to select exactly 50% of the nodes (if the number of nodes is odd we round the number of nodes to
be selected up) and form a Hamiltonian cycle (closed path) through this set of nodes such that the
sum of the total length of the path plus the total cost of the selected nodes is minimized.

\input{algorithms.tex}

\section{Results}

\input{scores.tex}

\input{times.tex}

\input{ls_runs.tex}

\subsection{TSPA.csv}

\input{TSPA.tex}

\subsection{TSPB.csv}

\input{TSPB.tex}

\newpage

\section{Conclusions}

We implemented a Hybrid Evolutionary Algorithm (HEA) with two different recombination operators and compared it against MSLS, ILS, and LNS.

Operator 1 (Common Edges + Random) combined with Local Search performed competitively but often struggled to find better optima than ILS/LNS within the same time budget, possibly due to the random reconstruction destroying too much structure.

Operator 2 (Filter + Repair) showed different behaviors. Without Local Search, it converged very quickly but to lower quality solutions compared to the LS-based methods. However, when combined with Local Search, it provided a robust mechanism for exploring the search space, though the high computational cost of the repair and LS steps limited the number of generations.

Overall, the hybrid approaches offer a good balance of diversification and intensification, but tuning the balance between the expensive local search and the population dynamics is crucial.

Link to the source code:

\url{https://github.com/markopolo139/Evolutionary-computation-put/tree/main/ass9}

The best solutions were checked with the provided solution checker.

\end{document}
