\section{Local Search Algorithms}

The following section describes the local search algorithms used to solve the TSP instances. The 2 different methods implemented are combinations of two main local search strategies (Steepest and Candidate) and random starting solution generation.

\subsection{Local Search Strategies}

Two main local search strategies were implemented: Steepest Local Search and Candidate Moves Local Search.

\begin{algorithm}
\caption{Steepest Local Search}
\label{alg:steepest_ls}
\begin{algorithmic}[1]
\Require Initial solution $S$, Neighborhood structure $N(S)$
\Ensure Optimized solution $S$
\State $improvement \gets \text{true}$
\While{$improvement$}
    \State $improvement \gets \text{false}$
    \State Find move $m^* \in N(S)$ that maximizes $-\Delta(m)$
    \If{$\Delta(m^*) < 0$}
        \State $S \gets \text{apply\_move}(S, m^*)$
        \State $improvement \gets \text{true}$
    \EndIf
\EndWhile
\State \Return $S$
\end{algorithmic}
\end{algorithm}

\begin{algorithm}
\caption{Candidate Moves Local Search}
\label{alg:candidate_ls}
\begin{algorithmic}[1]
\Require Initial solution $S$, Neighborhood structure $N(S)$, Candidate List $C$
\Ensure Optimized solution $S$
\State $improvement \gets \text{true}$
\While{$improvement$}
    \State $improvement \gets \text{false}$
    \State Find move $m^* \in N(S)$ that maximizes $-\Delta(m)$ where at least one node of the move is in the candidate list $C$
    \If{$\Delta(m^*) < 0$}
        \State $S \gets \text{apply\_move}(S, m^*)$
        \State $improvement \gets \text{true}$
    \EndIf
\EndWhile
\State \Return $S$
\end{algorithmic}
\end{algorithm}

\newpage

\subsection{Neighborhood Structures}

The neighborhood of a solution is defined by the set of possible moves that can be applied to it. Two types of neighborhood structures were used:

\begin{itemize}
    \item \textbf{Edge-based Neighborhood:}
    \begin{itemize}
        \item \textbf{Intra-route moves:} 2-opt moves, which consist of swapping two edges in the tour.
        \item \textbf{Inter-route moves:} Swapping any node in the solution with any node not in the solution.
    \end{itemize}
    \item \textbf{Candidate Moves Neighborhood:}
    \begin{itemize}
        \item The neighborhood is pruned by only considering moves where at least one of the nodes is in a pre-computed candidate list. The candidate list for a node $u$ contains the $k$ nearest neighbors of $u$.
    \end{itemize}
\end{itemize}

\subsection{Starting Solutions}

Random starting solutions were used for the local search algorithms:

\begin{itemize}
    \item \textbf{Random Start:} A random solution is generated by shuffling all available points and selecting the first half.
\end{itemize}

\subsection{Implemented Methods}

The 2 implemented methods are:

\begin{itemize}
    \item ls\_steepest\_edges\_random: Steepest search with an edge-based neighborhood and a random starting solution.
    \item ls\_candidate\_random: Steepest search with a candidate moves neighborhood and a random starting solution.
\end{itemize}