\documentclass{article}

\usepackage[english]{babel}
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{ragged2e}

\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsmath}

\title{Evolutionary Computation - Assignment 3}
\author{
  Patryk Janiak\\
  \texttt{156053}
  \and
  Marek Seget\\
  \texttt{156042}
}

\begin{document}
\maketitle

\section{Problem description}
We are given three columns of integers with a row for each node. The first two columns contain x
and y coordinates of the node positions in a plane. The third column contains node costs. The goal is
to select exactly 50\% of the nodes (if the number of nodes is odd we round the number of nodes to
be selected up) and form a Hamiltonian cycle (closed path) through this set of nodes such that the
sum of the total length of the path plus the total cost of the selected nodes is minimized.

\input{algorithms.tex}

\section{Results}

\input{scores.tex}

\input{times.tex}

\subsection{TSPA.csv}

\input{TSPA.tex}

\subsection{TSPB.csv}

\input{TSPB.tex}

\newpage

\section{Conclusions}

The local search algorithms, particularly those employing a greedy initial solution, demonstrate a significant improvement over simple constructive heuristics. The quality of the starting solution is crucial, as evidenced by the consistently better performance of methods with a greedy start compared to a random start.

Among the neighborhood structures, the edge-based neighborhood (2-opt) proves to be more effective and efficient than the node-based neighborhood. This is reflected in both the solution quality and the computation times.

The `ls\_steepest\_edges\_greedy` method stands out as the most effective algorithm, achieving the best scores for both TSPA and TSPB instances while also being one of the fastest. This suggests that a steepest search strategy combined with an edge-based neighborhood and a good initial solution is a powerful combination for this problem.

In general, the results highlight the importance of a well-chosen combination of initial solution generation, neighborhood structure, and search strategy for solving the TSP effectively.

Link to the source code:

\url{https://github.com/markopolo139/Evolutionary-computation-put/tree/main/ass3}

The best solutions were checked with the provided solution checker.

\end{document}
