\section{Local Search Algorithms}

The following section describes the local search algorithms used to solve the TSP instances. The 8 different methods implemented are combinations of two main local search strategies (Steepest and Greedy), two different neighborhood definitions (Node-based and Edge-based), and two different starting solution generation methods (Random and Greedy Construction).

\subsection{Local Search Strategies}

Two main local search strategies were implemented: Steepest Local Search and Greedy Local Search.

\begin{algorithm}
\caption{Steepest Local Search}
\label{alg:steepest_ls}
\begin{algorithmic}[1]
\Require Initial solution $S$, Neighborhood structure $N(S)$
\Ensure Optimized solution $S$
\State $improvement \gets \text{true}$
\While{$improvement$}
    \State $improvement \gets \text{false}$
    \State Find move $m^* \in N(S)$ that maximizes $-\Delta(m)$
    \If{$\Delta(m^*) < 0$}
        \State $S \gets \text{apply\_move}(S, m^*)$
        \State $improvement \gets \text{true}$
    \EndIf
\EndWhile
\State \Return $S$
\end{algorithmic}
\end{algorithm}

\begin{algorithm}
\caption{Greedy Local Search}
\label{alg:greedy_ls}
\begin{algorithmic}[1]
\Require Initial solution $S$, Neighborhood structure $N(S)$
\Ensure Optimized solution $S$
\State $improvement \gets \text{true}$
\While{$improvement$}
    \State $improvement \gets \text{false}$
    \State Randomly shuffle the order of moves in $N(S)$
    \For{each move $m$ in the shuffled neighborhood}
        \If{$\Delta(m) < 0$}
            \State $S \gets \text{apply\_move}(S, m)$
            \State $improvement \gets \text{true}$
            \State \textbf{break}
        \EndIf
    \EndFor
\EndWhile
\State \Return $S$
\end{algorithmic}
\end{algorithm}

\newpage

\subsection{Neighborhood Structures}

The neighborhood of a solution is defined by the set of possible moves that can be applied to it. Two types of neighborhood structures were used:

\begin{itemize}
    \item \textbf{Node-based Neighborhood:}
    \begin{itemize}
        \item \textbf{Intra-route moves:} Swapping any two nodes within the solution.
        \item \textbf{Inter-route moves:} Swapping any node in the solution with any node not in the solution.
    \end{itemize}
    \item \textbf{Edge-based Neighborhood:}
    \begin{itemize}
        \item \textbf{Intra-route moves:} 2-opt moves, which consist of swapping two edges in the tour.
        \item \textbf{Inter-route moves:} Swapping any node in the solution with any node not in the solution.
    \end{itemize}
\end{itemize}

\subsection{Starting Solutions}

Two methods were used to generate the initial solutions for the local search algorithms:

\begin{itemize}
    \item \textbf{Random Start:} A random solution is generated by shuffling all available points and selecting the first half.
    \item \textbf{Greedy Start:} A solution is constructed using the \textit{Nearest Neighbor with Weighted Regret} heuristic.
\end{itemize}

\subsection{Implemented Methods}

The 8 implemented methods are combinations of the above strategies and structures:

\begin{itemize}
    \item ls\_steepest\_nodes\_random: Steepest search with a node-based neighborhood and a random starting solution.
    \item ls\_steepest\_nodes\_greedy: Steepest search with a node-based neighborhood and a greedy starting solution.
    \item ls\_steepest\_edges\_random: Steepest search with an edge-based neighborhood and a random starting solution.
    \item ls\_steepest\_edges\_greedy: Steepest search with an edge-based neighborhood and a greedy starting solution.
    \item ls\_greedy\_nodes\_random: Greedy search with a node-based neighborhood and a random starting solution.
    \item ls\_greedy\_nodes\_greedy: Greedy search with a node-based neighborhood and a greedy starting solution.
    \item ls\_greedy\_edges\_random: Greedy search with an edge-based neighborhood and a random starting solution.
    \item ls\_greedy\_edges\_greedy: Greedy search with an edge-based neighborhood and a greedy starting solution.
\end{itemize}