\documentclass{article}

\usepackage[english]{babel}
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{ragged2e}

\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsmath}

\title{Evolutionary Computation - Assignment 6}
\author{
  Patryk Janiak\\
  \texttt{156053}
  \and
  Marek Seget\\
  \texttt{156042}
}

\begin{document}
\maketitle

\section{Problem description}
We are given three columns of integers with a row for each node. The first two columns contain x
and y coordinates of the node positions in a plane. The third column contains node costs. The goal is
to select exactly 50\% of the nodes (if the number of nodes is odd we round the number of nodes to
be selected up) and form a Hamiltonian cycle (closed path) through this set of nodes such that the
sum of the total length of the path plus the total cost of the selected nodes is minimized.

\input{algorithms.tex}

\section{Results}

\input{scores.tex}

\input{times.tex}

\input{ls_runs.tex}

\subsection{TSPA.csv}

\input{TSPA.tex}

\subsection{TSPB.csv}

\input{TSPB.tex}

\newpage

\section{Conclusions}

Both MSLS and ILS algorithms are effective in finding high-quality solutions, outperforming previous methods. ILS consistently finds better solutions than MSLS for both TSPA and TSPB instances, although the difference is more significant for TSPB.

The results suggest that the balance between intensification (local search) and diversification (perturbation) in ILS is well-suited for this problem, leading to better solutions than the repeated random-start approach of MSLS.

Link to the source code:

\url{https://github.com/markopolo139/Evolutionary-computation-put/tree/main/ass6}

The best solutions were checked with the provided solution checker.

\end{document}
