\documentclass{article}

\usepackage[english]{babel}
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{ragged2e}

\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsmath}

\title{Evolutionary Computation - Assignment 7}
\author{
  Patryk Janiak\\
  \texttt{156053}
  \and
  Marek Seget\\
  \texttt{156042}
}

\begin{document}
\maketitle

\section{Problem description}
We are given three columns of integers with a row for each node. The first two columns contain x
and y coordinates of the node positions in a plane. The third column contains node costs. The goal is
to select exactly 50\% of the nodes (if the number of nodes is odd we round the number of nodes to
be selected up) and form a Hamiltonian cycle (closed path) through this set of nodes such that the
sum of the total length of the path plus the total cost of the selected nodes is minimized.

\input{algorithms.tex}

\section{Results}

\input{scores.tex}

\input{times.tex}

\input{ls_runs.tex}

\subsection{TSPA.csv}

\input{TSPA.tex}

\subsection{TSPB.csv}

\input{TSPB.tex}

\newpage

\section{Conclusions}

We did not manage to achieve better best solutions than with ILS but on average (and in worst case) the LNS with LS finds better solutions.

For destroy operation we tried several approaches: removing worst points in proportion to their weighted score (cost + distance); removing one long segment in proportion to its weighted score; removing sliding windows in proportion to their weighted scores. The best destroy operation turned out the be the last one mentioned.

We also tested the amount of nodes to remove from 20\% to 40\% and we obtained the best results with 40\% removal strength.

Link to the source code:

\url{https://github.com/markopolo139/Evolutionary-computation-put/tree/main/ass7}

The best solutions were checked with the provided solution checker.

\end{document}
